Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search

### 2021-06-24 docs/paper.tex
Improved TUSS-based introduction

	As was shown by Geiger et al.\cite{geiger2018}, in practical scenarios, only heuristic methods can solve TUSS instances.
	Such methods are suboptimal so given a TUSS instance, a found heuristic solution gives a (loose) upper bound for the optimal solution cost; solving an instance also shows its feasibility, although there might be feasible instances for which no heuristic solution is found.
	By defining instances for a set shunting yard, heuristic methods can be used to characterise lower-bounds on the capacity of the yard in terms of both instance feasibility and solution cost.
	Because the quality of found heuristic solutions cannot be estimated \cite{mulderij2020}, it cannot be known how close such lower-bounds for yard capacity are to the true capacity. 
	Combined with the fact that current upper-bounds for capacity are highly optimistic, this makes it difficult for rail companies to decide when to expand their shunting infrastructure.

	Mulderij et al. propose the multi-agent pathfinding (MAPF) problem, as described in \cite{stern2019}, extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation of (discretised) TUSS for finding better upper-bounds using an approach analogous to that outlined above \cite{mulderij2020}.
	For this to succeed, a way to optimally solve MAPFM instances is needed, where optimal is defined as minimizing the Sum of Individual Costs (SIC) objective.

>>>>

	In practical scenarios, only heuristic methods can solve TUSS instances \cite{geiger2018}. Such a heuristic is used at NS to determine the capacity of shunting yards, which is the number of units a yard can serve in a day. This is done by defining a set of instances for the yard and determining the number of units for which 95\% of instances can be solved by the heuristic within a set time-out \cite{ven2019}. A problem is that a subset of feasible TUSS instances is not solved by the heuristic, meaning that the found capacity can be lower than the true capacity. Combined with the fact that current upper-bounds for capacity are highly optimistic, this makes it difficult to decide when to expand shunting infrastructure. Mulderij et al. propose the multi-agent pathfinding (MAPF) problem, as described in \cite{stern2019}, extended with a matching subproblem (hereafter MAPFM) as a suitable relaxation of (discretised) TUSS for finding better upper-bounds using an approach analogous to that outlined above \cite{mulderij2020}.
	For this to succeed, a way to optimally solve MAPFM instances is needed, where optimal is defined as minimizing the Sum of Individual Costs (SIC) objective.
